---
title: "R Notebook"
output: html_notebook
---

Load libraries and external functions and set directories and filenames

```{r}
if (!require(sf)) install.packages("sf"); library(sf)
if (!require(plyr)) install.packages("plyr"); library(plyr)
if (!require(dplyr)) install.packages("dplyr"); library(dplyr)
if (!require(pbapply)) install.packages("pbapply"); library(pbapply)
if (!require(terra)) install.packages("terra"); library(terra)
if (!require(tidyr)) install.packages("tidyr"); library(tidyr)

source("ProcessingFunctions.R")

ProjectDirectory <- "D:\\Projects\\LWP\\OLW_AttenuationUncertainty"
ProjectDataDirectory <- file.path(ProjectDirectory,"Data")
GISDirectory <- file.path(ProjectDataDirectory,"GIS")

LakeFileName <- file.path(GISDirectory,"Lakes","LakesWithinCatchments.shp")
LakeCatchmentsFileName <- file.path(GISDirectory,"LakeCatchments")
```

The sediment data are provided in NZMG projection.

```{r}
#Load the catchment spatial data
Catchments <- vect(file.path(GISDirectory,"Catchments","Catchments.shp"))




#Load the sediment yield data for the North and South islands
SI_SedimentYield <- rast(unzip(file.path(ProjectDataDirectory,"NIWA_SedimentYieldGrid","Si_sedye.zip")))
NI_SedimentYield <- rast(unzip(file.path(ProjectDataDirectory,"NIWA_SedimentYieldGrid","Ni_sedye.zip")))
crs(SI_SedimentYield)<- "EPSG:27200"
crs(NI_SedimentYield)<- "EPSG:27200"

#Load the lake polygon data
LakePolygons <- vect(LakeFileName)

#Load the lake catchment data, if it exists
if(file.exists(LakeCatchmentFileName)){
  LakeCatchments <- vect(LakeCatchmentsFileName)
} else {
  print("LakeCatchmnetsFileName is wrong, or it doesn't exist and needs to be created 
  using the LakeCatchmentFileCreation chunk")
}

```

Function to build lake catchment polygon shape file
```{r, LakeCatchmentFileCreation, eval = FALSE}

#' A convenience function to find the catchment upstream of a vector of RECV2 nzsegment numbers
#'
#'LakeCatchmentCreator() creates a SpatVector object of polygon features of the catchments upstream of a vector of REC2.5 reach ID numbers (nzsegment, nzsgmnt or nzseg_v3 attribute) upstream of a reach.
#'@param RECV2Watersheds A simple features (sf)  polygon representation of the REC V2 watersheds), TO_NODE and FROM_NODE (or FROM_NO) attributes.
#'@parma Locations A vector of RECV2.5 nzsegment numbers. Defaults to Lake Pukaki and Lake Rotoaira outlet reaches.
#'@param RECV2GeoDatabaseFile Filename of the ESRI geodatabase with the RECV2.5 riverlines and watersheds
#'@param LakeCatchmentFileName File name to be used for the output ESRI Polygon shapefile of catchments
#'@author Tim Kerr, \email{Tim.Kerr@@Rainfall.NZ}
#'@return A SpatVector of catchment polygons
#'@keywords REC River Environment Classification

LakeCatchmentCreator <- function(Locations = c(13165194,3166693),
                                 RECV2GeoDatabaseFile = "nzRec2_v5.gdb",
                                 LakeCatchmentFileName = LakeCatchmentFileName){

  RiverNetwork <- sf::st_read(REC2V2GeoDatabase, layer = "riverlines")
  Watersheds <- sf::st_read(REC2V2GeoDatabase, layer = "rec2ws")
  
  LakeCatchmentsList <- pblapply(Locations, function(Location) {
    Catchment <- CatchmentCreator(Watersheds = Watersheds, ReachNetwork = RiverNetwork, OutletReach = Location)
    return(Catchment)
  })
  LakeCatchments <- do.call(rbind,LakeCatchmentsList)
  LakeCatchments$nzsegment <- names(LakeCatchmentsList)
  LakeCatchments <- vect(LakeCatchments)
  #Suspect a bug in the terra::writeVector function
  #Check for output file, delete it if it exists
  if (dir.exists(LakeCatchmentFileName)) unlink(LakeCatchmentFileName,recursive=TRUE)
  writeVector(x=LakeCatchments, filename=LakeCatchmentFileName,filetype = "ESRI Shapefile",overwrite=TRUE)
  return(LakeCatchments)
}

#LakeCatchments <- LakeCatchmentCreator(Locations = LakePolygons$RECV2Out,
                     RECV2GeoDatabaseFile = "D:\\Projects\\data\\RECV2.5\\nzRec2_v5.gdb",
                     LakeCatchmentFileName = LakeCatchmentFileName)
```

Work through each catchment, find which lakes are within them, get the catchments for those lakes and use their combined area to mask out what area is not to be used to aggregate the sediment yield gridded data
```{r}
Start_Time = Sys.time() #30 minutes for all catchments

#Find the lakes that are within each water quality measuring site catchment
#This returns a boolean matrix of catchments (rows) by lakes (columns)
LakesOfInterest <- relate(Catchments,LakePolygons,relation="contains")

#Work through each catchment, and erase the part that is in a lake catchment
LakeCorrectedCatchmentList <- lapply(seq(1,nrow(Catchments)), function(CatchmentIndex){
  #browser()
  WQCatchment_withoutLakeCatchments <- erase(Catchments[CatchmentIndex],LakeCatchments[LakesOfInterest[CatchmentIndex,]])
})

#two WQ sites are lake outlets!! So there is nothing left after erasing lake catchments.
CatchmentsWithNoPYield <- which(Catchments$nzsegment %in% LakePolygons$RECV2Out)

LakeCorrectedCatchments <- do.call(rbind,LakeCorrectedCatchmentList)

#Reproject to NZMG to enable use with the Sediment yield data
LakeCorrectedCatchmentsNZMG <- project(LakeCorrectedCatchments,y="EPSG:27200")

#Initialise a sediment yield attribute
LakeCorrectedCatchmentsNZMG$SedYield <- as.numeric(NA)


#Process the South Island and North Island separately 
#Find all the South Island catchments based on the RECV2 number
SICatchments <- which(LakeCorrectedCatchmentsNZMG$nzsegment %/% 1000000 >= 10 )#& LakeCorrectedCatchmentsNZMG$sID %in% CarolinesTestCatchments)
#Find the North Island catchments
NICatchments <- which(LakeCorrectedCatchmentsNZMG$nzsegment %/% 1000000 < 10 )# & LakeCorrectedCatchmentsNZMG$sID %in% CarolinesTestCatchments)

LakeCorrectedCatchmentsNZMG$SedYield[SICatchments] <- terra::extract(SI_SedimentYield,LakeCorrectedCatchmentsNZMG[SICatchments],sum, na.rm=TRUE)[,2]
LakeCorrectedCatchmentsNZMG$SedYield[NICatchments] <- terra::extract(NI_SedimentYield,LakeCorrectedCatchmentsNZMG[NICatchments],sum, na.rm=TRUE)[,2]

#Correct the units to account for the resolution of the sediment data (100 m)
LakeCorrectedCatchmentsNZMG$SedYield <- LakeCorrectedCatchmentsNZMG$SedYield / 100 #Should now be in Tons/Year

#Convert to a data frame, ready for exporting
CatchmentSedYield <- as.data.frame(LakeCorrectedCatchmentsNZMG)

#Add in the two lake-outlet catchments
MissingSites <- cbind(as.data.frame(Catchments)[CatchmentsWithNoPYield,],data.frame("SedYield" = c(0,0)))
CatchmentSedYield <- rbind.fill(CatchmentSedYield,MissingSites)

#Round the sediment yield to the nearest decimal place
CatchmentSedYield$SedYield <- round(CatchmentSedYield$SedYield,1)

write.table(CatchmentSedYield,
            file=file.path(ProjectDataDirectory,"SedimentYieldV0.csv"),sep=",",row.names = FALSE,append=FALSE,quote = FALSE)

End_time <- Sys.time()
End_time - Start_Time
```

Repeat the above for the test catchments and check that the results match what they should.
For the test catchments, the lake correction does not need to be applied, as it is only considered for the second "Chard" exmple, and only for one sub-catchment, which is at the Lake Wakatipu outlet, so has a sediment yield of 0
```{r, eval = FALSE}
#Load the test catchments supplied by NIWA (and edited and reprojected to NZTM by Tim) for checking sediment yield calculations
Bowens <- vect(file.path(ProjectDataDirectory,"NIWA_SedimentYieldGrid","sediment_2002","bowensNZTM.shp"))
Chards<- vect(file.path(ProjectDataDirectory,"NIWA_SedimentYieldGrid","sediment_2002","chardsNZTM.shp"))

TestYields <- c("Bowens"=1314600,"Chards"=1337000) #From the ReadMe.doc file that accompanied the sediment yield data. In Tons/year
LakeSubCatchments <- "Frankton"

invisible(lapply(seq_along(TestYields), function(TestIndex){
  
  TestCatchment <- names(TestYields[TestIndex])
  
  #Reproject to NZMG to enable use with the Sediment yield data
  CatchmentsNZMG <- project(get(TestCatchment),y="EPSG:27200")
  
  #Initialise a sediment yield attribute
  CatchmentsNZMG$SedYield <- as.numeric(NA)
  
  CatchmentsNZMG$SedYield <- terra::extract(SI_SedimentYield,CatchmentsNZMG,sum, na.rm=TRUE)[,2]
  
  #Remove the lake sub-catchments
  CatchmentsNZMG <- CatchmentsNZMG[!CatchmentsNZMG$SITENAME %in% LakeSubCatchments,]
  
  #Total the yield for the non-lake subcatchments
  TotalSedYield <- sum(CatchmentsNZMG$SedYield) / 100
  
  #Calculate the difference to the expected values, and report
  DifferencePct <- round((TotalSedYield - TestYields[TestIndex])/TestYields[TestIndex] * 100,2)
  
  print(paste(TestCatchment,"result is within",DifferencePct, "% of the expected"))
  return()
}))
```


