---
title: "R Notebook"
output: html_notebook
---

Load libraries and external functions

```{r}
if (!require(sf)) install.packages("sf"); library(sf)
if (!require(plyr)) install.packages("plyr"); library(plyr)
if (!require(dplyr)) install.packages("dplyr"); library(dplyr)
if (!require(pbapply)) install.packages("pbapply"); library(pbapply)
if (!require(terra)) install.packages("terra"); library(terra)
if (!require(tidyr)) install.packages("tidyr"); library(tidyr)

source("ProcessingFunctions.R")
```

Set Directories and file names
```{r}

ProjectDirectory <- "D:\\Projects\\LWP\\OLW_AttenuationUncertainty"
ProjectDataDirectory <- file.path(ProjectDirectory,"Data")
GISDirectory <- file.path(ProjectDataDirectory,"GIS")

LeachRateLUTFile <- file.path(ProjectDataDirectory,"LandUseToLossRatesV0.csv")

```

Create default Catchment-scale and Farm-scale grids that cover the country.
CAtchment scales grid are 10 km x 10 km squares with the bottom left hand corner at
NZTM coordinate Easting=1000000 Northing=4700000
Topright at Easting=2100000, Northing=6200000

FarmScale are 250 m x 250 m scale grid aligned to the CatchmentScale Grid
We need a grid with FarmScale rows within each CatchmentScaleCell, one with columns within each catchmentScaleCell, and one with CatchmentScale row number, and one with CatchmentScaleColumn Number
```{r}
ExtentCoordinates <- data.frame("Easting"=c(1000000,2100000),"Northing"=c(4700000,6200000))
ExtentPolygon <- ExtentCoordinates %>% 
  st_as_sf(coords = c("Easting","Northing"),crs= "epsg:2193") %>%
  st_bbox() %>%
  st_as_sfc()

CatchmentScaleResolution <- 10000
CatchmentScaleGrid <- rast(vect(ExtentPolygon),resolution = CatchmentScaleResolution,vals=1)
CatchmentScaleGridRow <- rast(CatchmentScaleGrid,vals=nrow(CatchmentScaleGrid)+1-rowFromCell(CatchmentScaleGrid,cells(CatchmentScaleGrid)))
CatchmentScaleGridColumn <- rast(CatchmentScaleGrid,vals=colFromCell(CatchmentScaleGrid,cells(CatchmentScaleGrid)))

CatchmentScalePolygonGrid <-sf::st_as_sf(st_make_grid(vect(ExtentPolygon), 
                                          cellsize = CatchmentScaleResolution))

#This next line gets the centroid coordinates of each polygon, subtracts the bottom left coordinates and half the cell resolution, converts them to km, and and adds 1 (to keep indexing from 1) and converts to a fixed width format
NumericIDs <- st_centroid(st_geometry(CatchmentScalePolygonGrid)) %>% st_coordinates() %>% as.data.frame() %>% mutate(across(1,~((. - ExtentCoordinates$Easting[1] - CatchmentScaleResolution/2) / 10000 + 1))) %>% 
  mutate(across(2,~((. - ExtentCoordinates$Northing[1] - CatchmentScaleResolution/2) / 10000 + 1))) %>% 
  mutate_all(~sprintf("%03g",.))

CatchmentScalePolygonGrid$CSID <- paste0("CS",apply(NumericIDs,1,paste,collapse=""))

CatchmentScalePolygonGrid %>% st_write(file.path(GISDirectory,"SrinivasanTypes.gpkg"),layer = "CatchmentScaleGrid", delete_layer = TRUE)

FarmScaleResolution <- 250
FarmScaleGrid <- rast(vect(ExtentPolygon),resolution = FarmScaleResolution,vals=1)

#I want to number cells from 1 to 40 in rows (bottom to top) and columns (left to right) within each CatchmentScale grid
RowIDs <- 41 - (rowFromCell(FarmScaleGrid,cells(FarmScaleGrid)) %% 40)
RowIDs[RowIDs==41] <- 1
FarmScaleGridRow <- rast(FarmScaleGrid,vals=RowIDs)

ColumnIDs <- colFromCell(FarmScaleGrid,cells(FarmScaleGrid)) %% 40
ColumnIDs[ColumnIDs == 0] <- 40
FarmScaleGridColumn <- rast(FarmScaleGrid,vals=ColumnIDs)

FarmScaleCSRow <- disagg(CatchmentScaleGridRow,fact=40,method="near")
FarmScaleCSColumn <- disagg(CatchmentScaleGridColumn,fact=40,method="near")

FarmScaleStack <- rast(list("FSRow"=FarmScaleGridRow,"FSCol"=FarmScaleGridColumn,"CSRow"=FarmScaleCSRow,"CSCol"=FarmScaleCSColumn))
```



Create the catchment polygon shape files for the water quality observation locations
```{r,eval = FALSE}
#Load the watershed and river network data. Note that these are large.
#The RECV2 geodatabase. version  from Ton with correct attribute names.
REC2V2GeoDatabase <- "D:\\Projects\\data\\RECV2.5\\nzRec2_v5.gdb" #This is the NIWA version

RiverNetwork <- sf::st_read(REC2V2GeoDatabase, layer = "riverlines")
Watersheds <- sf::st_read(REC2V2GeoDatabase, layer = "rec2ws")

#Load the Site data. Provided by Ton as RData files. One for TN and one for TP, but 
# both load a data frame called "BestLoads", and both (supposedly) with the same reach ID's
load(file.path(ProjectDataDirectory,"BestTNloads_22May17_y2020.rdata"))
Locations <- BestLoads$nzsegment
names(Locations) <- BestLoads$sID

remove(BestLoads)

CatchmentList <- pblapply(Locations, function(Location) {
  Catchment <- CatchmentCreator(Watersheds = Watersheds, ReachNetwork = RiverNetwork, OutletReach = Location)
  return(Catchment)
})
Catchments <- do.call(rbind,CatchmentList)
Catchments$sID <- names(CatchmentList)
st_write(Catchments,dsn = file.path(GISDirectory,"Catchments"),driver = "ESRI Shapefile",append = FALSE)


#Clear out some space
remove("BestLoads","RiverNetwork","Watersheds")

#Plot the result as a check it is right
plot(st_geometry(Catchments))
```


Reclass the LCDBV5 and save
```{r,eval = FALSE}
#Takes 90 minutes!
Start_time = Sys.time()

#The LCDBV5 geodatabase. version  from downloaded from LRIS 
LCDBV5GeoDatabase <- "D:\\Projects\\data\\LCDBV5\\lcdb-v50-land-cover-database-version-50-mainland-new-zealand.gdb"

#This takes ~1 minute to load and gives a warning that can be ignored
LCDBV5 <- sf::st_read(LCDBV5GeoDatabase)

#Remove the "Not land" polygons. These are areas that were land in previous versions og the LCDBV5 but no longer are
#They are usually coastal areas that have eroded. There are 14 of these polygons.
LCDBV5 <- LCDBV5[!LCDBV5$Name_2018 == "Not land",]

#The Dairy areas
MonaghanGeoDatabase <- "D:\\Projects\\data\\OLWNutrientExportSpatialFiles\\Export_MfE.gdb"

#Load the dairy areas, and union into a single MultiPolygon, this takes time...30 s
MonaghanDairy <- sf::st_read(MonaghanGeoDatabase,layer = "TypologiesDairy") %>% st_union()

#Give it a "Dairy" attribute set to TRUE
Dairy <- data.frame(Dairy = TRUE)
st_geometry(Dairy) <- MonaghanDairy

#Load the LCDBV5-to-Srinivasan reclass table
LandUseLookupTable <- read.csv(file.path(ProjectDataDirectory,"LCDBV5ReclassTable.csv"))

#And reclass the LCDBV5
ReclassedLCDBV5 <- merge(LCDBV5,LandUseLookupTable[,c("Class_2018","SrinivasanLandUse")],all.x=TRUE)

#dissolve the polygons
ReclassedLCDBV5 <- ReclassedLCDBV5 %>% select(SrinivasanLandUse) %>% group_by(SrinivasanLandUse) %>% summarise()

#GISUnion the reclassed LCDBV5 with the Dairy areas
LandUsePlusDairy <- GISunion(ReclassedLCDBV5,Dairy)

#LCDV5 pasture is considered Sheep and Beef unless Monaghan thinks it's Dairy
LandUsePlusDairy$SrinivasanLandUse[LandUsePlusDairy$SrinivasanLandUse == "Pasture"] <- "Sheep and Beef"
LandUsePlusDairy$SrinivasanLandUse[!is.na(LandUsePlusDairy$Dairy)] <- "Dairy"

plot(LandUsePlusDairy[,"SrinivasanLandUse"],border=NA, key.width = lcm(4.5))

#Rename the columns prior to saving, otherwise the ESRI driver will shorten them to 8 letters using its own system
LandUsePlusDairy <- LandUsePlusDairy %>% rename(LandUse = SrinivasanLandUse)

LandUsePlusDairy %>% st_write(file.path(GISDirectory,"SrinivasanTypes.gpkg"),layer = "LandUse", delete_layer = TRUE)

End_Time = Sys.time()
End_Time - Start_time

#Clear out some more space
remove("MonaghanDairy","LCDBV5","LandUsePlusDairy")

```

Now need to do slope
```{r,eval = FALSE}
#Takes 2 minutes
Start_time = Sys.time()

#The LRI Slope geodatabase. version  from downloaded from LRIS
#Better to get the GeoPackage version as that is an Open data format.
LRIGeoDatabase <- "D:\\Projects\\data\\LRI\\Slope\\nzlri-slope.gdb"
LRISlope <- sf::st_read(LRIGeoDatabase)

SlopeLookupTable <- read.csv(file.path(ProjectDataDirectory,"LRISlopeReclassTable.csv"))

LRISlope <- merge(LRISlope,SlopeLookupTable[,c("LRI..SLOPE1S..Class.ID","Srinivasan.slope.type")],
                  by.x = "SLOPE1S",by.y = "LRI..SLOPE1S..Class.ID",all.x=TRUE)
LRISlope$Srinivasan.slope.type[is.na(LRISlope$Srinivasan.slope.type)] <- "Flat"
Slope <- LRISlope %>% select(Srinivasan.slope.type) %>% group_by(Srinivasan.slope.type) %>% summarise()
#st_write(Slope,dsn = file.path(GISDirectory,"Slope"),driver = "ESRI Shapefile",append = FALSE)
Slope %>% st_write(file.path(GISDirectory,"SrinivasanTypes.gpkg"),layer = "Slope", delete_layer = TRUE)

#Plot the result as a check it is right
plot(Slope[,"Srinivasan.slope.type"],border=NA, key.width = lcm(4.5))

End_Time = Sys.time()
End_Time - Start_time

#Clear out some more space
remove("LRISlope","Slope")
```

Now do  moisture
```{r,eval = FALSE}
#Takes 45 seconds
Start_time = Sys.time()

#The MfE Irrigated area geodatabase. version downloaded from MfE Data portal 
IrrigationGeoDatabase <- "D:\\Projects\\data\\MfE\\Irrigation\\irrigated-land-area-raw-2020-update.gdb"
Irrigation<- sf::st_read(IrrigationGeoDatabase)

#Fix any issues with the geometry
Irrigation <- st_make_valid(Irrigation)

#Create an attribute explicitly set to TRUE useful for the later union with the rain data
Irrigation$Irrigated <- TRUE
Irrigation <- Irrigation[,c("Irrigated")]

#Merge all the adjoining polygons together takes 30 s. Do not convert from  MultiPolygons to Polygons as this stops my GISUnion function from working
Irrigation <- Irrigation %>% select(Irrigated) %>% group_by(Irrigated) %>% dplyr::summarise()

#Prepare the rain data
RainfallFile <- "D:\\Projects\\data\\MfE\\Rain19722016\\totann7216.tif" #Note that this is in NZMG projection.

RainfallRaster <- rast(RainfallFile)

#Reclassify <1100, 1100-1700, >1700
RainReclassMatrix <- matrix(c(0,1100,1,
                       1100,1700,2,
                       1700,30000,3), ncol=3, byrow=TRUE)
ClassifiedRain <- classify(RainfallRaster, rcl = RainReclassMatrix, include.lowest = TRUE)

#Convert to polygons
PolygonisedRain <- sf::st_as_sf(as.polygons(ClassifiedRain))
PolygonisedRain <- st_make_valid(PolygonisedRain)
#Reproject to NZTM
PolygonisedRain <- st_transform(PolygonisedRain, crs=2193)
PolygonisedRain$Srinivasan.Moisture.Type <- c("Dry","Moist","Wet")[PolygonisedRain$totann7216]

#Union with irrigation takes time.. about a minute....
Moisture <- GISunion(PolygonisedRain,Irrigation)

#Set all Irrigated polygons to have a moisture class of "Irrigated"
Moisture$Srinivasan.Moisture.Type[Moisture$Irrigated] <- "Irrigated"

#st_write(Moisture,dsn = file.path(GISDirectory,"Moisture"),driver = "ESRI Shapefile",append = FALSE)
Moisture %>% st_write(file.path(GISDirectory,"SrinivasanTypes.gpkg"),layer = "Moisture", delete_layer = TRUE)

plot(Moisture[,"Srinivasan.Moisture.Type"],border=NA, key.width = lcm(4.5))

End_Time = Sys.time()
End_Time - Start_time

#Clear out some space
remove("Irrigation","RainfallRaster","PolygonisedRain","Moisture")
```

Load a catchment, intersect the land use, slope and moisture
Lookup the srinivasan TP and TN
Calculate total TP and TN, as well as contributions from each land use type
Provide totals and contributions of nutrients, as well as area.
```{r}
#Load the Srinivasan Land Use, Moisture and Slope type's spatial data
LandUse <- st_read(file.path(GISDirectory,"SrinivasanTypes.gpkg"),layer = "LandUse")
Slope <- st_read(file.path(GISDirectory,"SrinivasanTypes.gpkg"),layer = "Slope")
Moisture <- st_read(file.path(GISDirectory,"SrinivasanTypes.gpkg"),layer = "Moisture")

#Load the catchment spatial data
Catchments <- st_read(dsn = file.path(GISDirectory,"Catchments","Catchments.shp"))

#Load the nutrient loss rate coefficient look-up data
NutrientLookupTable <- read.csv(LeachRateLUTFile)


```


```{r}
Start_Time = Sys.time()

#Initialise an empty output dataframe
if (exists("NutrientOutputData")) rm(NutrientOutputData)
NutrientOutputData       <- data.frame(NULL)
FarmScaleMetadata        <- data.frame(NULL)
CatchmentScaleMetadata   <- data.frame(NULL)
WaterQualitySiteMetadata <- data.frame(NULL)
#work through each catchment using a for loop as the apply doesn't work well with sf objects
#For all Catchments this takes 3 Hours!!
#Test catchments requested by Caroline are Tukituki,Ruamahanga and Hurunui, which have sID's of
#HBRC-00043_NIWA, GW-00033 and NRWQN-00059_NIWA respectively which are indices 140,156 and 300

for (WaterQualitySite in Catchments$sID[c(140,156,300)] ){
  print(WaterQualitySite)
  print(paste(which(WaterQualitySite==Catchments$sID),"of",nrow(Catchments)))
  Catchment <- Catchments[Catchments$sID == WaterQualitySite,]
  CatchmentArea <- st_area(Catchment) %>% units::set_units(NULL) / 10000
  
  WaterQualitySiteMetadata <- data.frame("sID"=Catchment$sID,
                                         "Hectares"=CatchmentArea,
                                         "nzsegment"=Catchment$nzsegment)
  

  
  #Subset and intersect the Srinivasan spatial data to just the catchment.
  #Seems to need removal of any existing CatchmentLandUse object before it is re-created
  if (exists("CatchmentLandUse")) rm(CatchmentLandUse)
  
  #Note that the intersections raise a warning:
  #"attribute variables are assumed to be spatially constant throughout all geometries"
  #This can be suppressed (see https://github.com/r-spatial/sf/issues/406)
  #By explicitly defining the attributes of the contributing geometries as constant
  #Or by only intersecting the geometries, then -re-attaching the attributes
  #I don't understand this and need to figure out what is meant.
  #But I think I can do the explicit solution.
  CatchmentLandUse <- st_intersection(Catchment,LandUse)
  CatchmentLandUseSlope <- st_intersection(CatchmentLandUse,Slope)
  CatchmentLandUseSlopeMoisture <- st_intersection(CatchmentLandUseSlope,Moisture)
  
  # #Get the area of each typology and set the units to hectares, but clear the units attribute to avoid managing units later on
  # CatchmentLandUseSlopeMoisture$area.ha <- st_area(CatchmentLandUseSlopeMoisture) %>% units::set_units(NULL)  / 10000
  # 
  # #Use the look up table to define TP and TN for each srinivasan class
  CatchmentLandUseSlopeMoisture <- merge(CatchmentLandUseSlopeMoisture,NutrientLookupTable,by.x = c("Srinivasan.slope.type","Srinivasan.Moisture.Type","LandUse"),by.y = c("Slope","Moisture","LandUse"))
  
  #Sometimes the intersections result in lines, so just extract the polygons. If you don't then 
  #you can't convert the resulting sf to a SpatVector type, as they don't handle mixed types.
  CatchmentLandUseSlopeMoisture <- st_collection_extract(CatchmentLandUseSlopeMoisture, "POLYGON")
  
  #do the remaining processing as rasters
  
  #Intersect the FarmScale raster stack with the catchment
  FarmScaleMasked <- mask(FarmScaleStack,vect(Catchment)) %>% crop(vect(Catchment))
  #FarmScaleUniqueID <- rast(FarmScaleMasked[[1]],vals=seq(1,ncell(FarmScaleMasked[[1]])))
  
  #Convert to a high resolution (25 m) raster of Srinivasan Type
  #Need to convert the Srinivasan Type to a factor so that we know what the raster values are
  HighResGrid <- rast(ext(FarmScaleMasked),resolution= 25, vals=1)
  CatchmentLandUseSlopeMoisture$Type <- as.factor(CatchmentLandUseSlopeMoisture$Type)
  
  #The next line converts the "Type" polygon shape file into a raster with numbers from 0 to length(Type)-1 
  #representing the Type factors. That is, the raster values are the factor levels - 1.
  #This was not obvious to me.
  TypeGrid <- rasterize(vect(CatchmentLandUseSlopeMoisture),y=HighResGrid,field="Type")
  
  #Get the names of the unique Types in this catchment
  Types <- levels(CatchmentLandUseSlopeMoisture$Type)

  #Build a stack of single-Type rasters
  TypeStack <- lapply((0:(length(Types)-1)),function(x) {TypeGrid %in% x}) %>% rast()
  names(TypeStack) <- Types
  #Aggregate each layer to the FarmScale unit (i.e. 6.25 hectaes, which is 10 x the high resolution scale)
  AggregateStack <-lapply(TypeStack,function(SingleType){
    aggregate(SingleType,fact=10,fun='sum')
  }) %>% rast()
  
  CatchmentGrid <- values(AggregateStack, dataframe=TRUE)
  CatchmentGrid$sID <- Catchment$sID
  CatchmentGrid$FSRow <- values(FarmScaleMasked$FSRow)
  CatchmentGrid$FSCol <- values(FarmScaleMasked$FSCol)
  CatchmentGrid$CSRow <- values(FarmScaleMasked$CSRow)
  CatchmentGrid$CSCol <- values(FarmScaleMasked$CSCol)
  
  #Go from wide to long
  CatchmentLong <- pivot_longer(CatchmentGrid,Types,names_to="Type",values_to = "Cells")
  CatchmentLong <- CatchmentLong[CatchmentLong$Cells > 0,]
  
  #Add TN and TP loss rates from lookup table
  CatchmentLong <- merge(CatchmentLong,NutrientLookupTable[,c("Type","TN.Loss.Rate","TP.Loss.Rate")],by.x = c("Type"),by.y = c("Type"))
  
  #Parse out the land use, moisture class and slope
  CatchmentLong$Srinivasan.slope.type <- strsplit(CatchmentLong$Type,"[-]")[[1]][2]
  CatchmentLong$Srinivasan.Moisture.Type<- strsplit(CatchmentLong$Type,"[-]")[[1]][3]
  CatchmentLong$LandUse<- strsplit(CatchmentLong$Type,"[-]")[[1]][1]
  
  #Calculate area
  CatchmentLong$Hectares <- CatchmentLong$Cells * 0.0625
  
  #Devise UniqueFarmScaleID
  CatchmentLong$FSID <- paste0("FS",sprintf("%02g",CatchmentLong$FSCol),
                          sprintf("%02g",CatchmentLong$FSRow))
  CatchmentLong$CSID <- paste0("CS",sprintf("%03g",CatchmentLong$CSCol),
                          sprintf("%03g",CatchmentLong$CSRow))
  CatchmentLong$UniqueID <- paste0(CatchmentLong$sID,"_",CatchmentLong$CSID,CatchmentLong$FSID)
  #Drop some of the columns
  CatchmentLong <- CatchmentLong %>% select(!c(FSRow,FSCol,CSRow,CSCol,Cells))
  
  #Re-order columns
  CatchmentLong <- CatchmentLong[,c("UniqueID","sID","CSID","FSID","Hectares",
                                    "Type","LandUse","Srinivasan.slope.type","Srinivasan.Moisture.Type",
                                    "TN.Loss.Rate","TP.Loss.Rate")]
  
# #Ditch the geometry to make further processing easier
#   rm(CatchmentData)
#   CatchmentData <- st_drop_geometry(CatchmentLandUseSlopeMoisture)
#   
#   #Calculate load for each polygon
#   CatchmentData$TN.Load <- CatchmentData$TN.Loss.Rate * CatchmentData$area.ha
#   CatchmentData$TP.Load <- CatchmentData$TP.Loss.Rate * CatchmentData$area.ha
# 
#   #Group and summarise on Land Use
#   CatchmentLandUseData <- CatchmentData %>% group_by(LandUse) %>% 
#     summarise(areaPct = sum(area.ha)/CatchmentArea,area.ha = sum(area.ha),sID = first(sID),nzsegment=first(nzsegment),
#               TN = sum(TN.Load)/sum(area.ha),TP = sum(TP.Load)/sum(area.ha))
#   
# 
#   CatchmentWide <- pivot_wider(CatchmentLandUseData,
#                                id_cols = c(sID,nzsegment),
#                                names_from=LandUse,
#                                values_from = c(area.ha,TN,TP),
#                                names_glue = "{LandUse}_{.value}")
#   
#   CatchmentWide$area.ha <- CatchmentArea
#   CatchmentWide$TNLoad <- sum(CatchmentData$TN.Load)
#   CatchmentWide$TPLoad <- sum(CatchmentData$TP.Load)
#   CatchmentWide$TNLossRate <- (CatchmentWide$TNLoad / CatchmentArea) 
#   CatchmentWide$TPLossRate <- (CatchmentWide$TPLoad / CatchmentArea) 

  
  NutrientOutputData <- dplyr::bind_rows(NutrientOutputData,CatchmentLong)
  #write to a csv file

}
End_Time = Sys.time()
End_Time - Start_Time

write.table(NutrientOutputData,file=file.path(ProjectDataDirectory,"OutputV2.csv"),sep=",",row.names = FALSE,append=TRUE,quote = FALSE)
```


```{r}
#Create a function that builds a metadata file of unique FarmScale units, CatchmentScale Units and Water Quality Site Catchments.

MetadataCreator <- function(OutputData = NutrientOutputData, WaterQualitySiteData = Catchments){
  FarmScaleMetadata <- OutputData %>% group_by(UniqueID) %>% summarise(Hectares = sum(Hectares), sID = first(sID), CSID = first(CSID), FSID = first(FSID))
  FarmScaleMetadata$NZTM_Easting <- as.numeric(substr(FarmScaleMetadata$CSID,3,5)) * 10000 -10000 + 1000000 + as.numeric(substr(FarmScaleMetadata$FSID,3,4)) * 250 -250 + 125
  FarmScaleMetadata$NZTM_Northing <- as.numeric(substr(FarmScaleMetadata$CSID,6,8)) * 10000 -10000 + 4700000 + as.numeric(substr(FarmScaleMetadata$FSID,5,6)) * 250 -250 + 125
  
  CatchmentScaleMetadata <- OutputData %>% group_by(CSID) %>% summarise(CSID = first(CSID))
  CatchmentScaleMetadata$NZTM_Easting <- as.numeric(substr(CatchmentScaleMetadata$CSID,3,5)) * 10000 -10000 + 1005000
  CatchmentScaleMetadata$NZTM_Northing <- as.numeric(substr(CatchmentScaleMetadata$CSID,6,8)) * 10000 - 10000 + 4705000
  
  WaterQualitySiteData$Hectares <- st_area(Catchments) %>% units::set_units(NULL) / 10000
  WaterQualitySiteMetaData <- st_drop_geometry(Catchments)
  
  Metadata = list(FarmScale = FarmScaleMetadata, 
                  CatchmentScale = CatchmentScaleMetadata, 
                  WaterQualitySites = WaterQualitySiteMetaData)
}

MetaDataList <- MetadataCreator()

write.table(MetaDataList[["FarmScale"]],file=file.path(ProjectDataDirectory,"FarmScaleMetadata.csv"),sep=",",row.names = FALSE,quote = FALSE)
write.table(MetaDataList[["CatchmentScale"]],file=file.path(ProjectDataDirectory,"CatchmentScaleMetadata.csv"),sep=",",row.names = FALSE,quote = FALSE)
write.table(MetaDataList[["WaterQualitySites"]],file=file.path(ProjectDataDirectory,"WaterQualitySiteMetaData.csv"),sep=",",row.names = FALSE,quote = FALSE)

```